A thesis draft

### 2018-10-09 draft.tex
Remove TODO
Add IP over IP image, create misc folder for draw.io source files

As in~\ref{chap:intro}, the creation of a full ETSI MANO compliant
architecture, following the suggestions described in RFC 7665, require the 
integration of multiple tools (some of them have been already briefly 
introduced in~\ref{chap:intro}). The tools were choosen after their 
analysis, where pro and cons have been studied and compared to the necessity of 
this thesis. Since the project has been developed with the cloud provided by 
the University of Padua, Openstack (which a product analysis can be found later 
in~\ref{chap:prjan:sec:openstack}) has been used as base for our deployments.

@@

As today, when a packets gets send from a seder $S$, to a receiver $R$, the 
packet gets travelling to te backbone receive appropriate in-hardware packet 
processing before being received by $R$. During this elaboration, it is 
important to maintain the transparency of the connection, so that the network 
users are not aware of the packets elaboration at all. To perform that, many 
solutions are available: TUN/TAP packet incapsulation, IP over IP or TCP 
session recreation\todo{Check if it's the same of Split TCP}.

TUN/TAP and IP over IP maintain the connection transparency incapsulating the
packet in another one. In this way, the original packet remains preserved and it
becomes the new packet payload\todo{Make an image showing a packet inside
  another packet, to make easy to understand what we're meaning here}, that can
be elaborated and modified accordingly, until it gets decapsulated and sent to
$R$ eventually. When $R$ receives the packet, it is not be aware of the packet
elaboration, since all the original headers were preserved (or slightly
modified). TCP session recreation, instead, ``split'' the TCP session in two
endpoints: an Ingress, that manage the connection with the client and an Egress,
that communicate with the packet receiver creating a multi-overlay-hop path
where for each hop there is an possible indipendent TCP connection. In order to
achieve that, a session table needs to be established and continuously updated,
while TCP headers need to be accordingly modified to allow data transmission
through the Ingress and Egress points. Nonetheless, care should be given to
packets path: in order to avoid ill-calculated congestion windows, the incoming
packets need to follow the same (or an equivalent one) path for the same
instatiated connection. This phenomenom is based on the intermediate proxies
that create the route: it is the case, for example, when an intermediate node
sends back a spoofed ACK before the original packet is delivered to the real
consegnee. In this senario, the sender, unaware of the proxy, will miscalculate
the sending window based on the too low RTT. Other problems of TCP splitting are
reliability and security, especially because the end to end TCP logic is no
longer maintained: a server failure may cause to an unaware client to believe
that all the packets have reached the destination. TCP session recreation seems
burdersome and it doesn't seem to add any significant benefit at the first
sight, but it offers the flexibility to perform extensive packet manipulation:
since the packet its recreated every time at the Ingress and Egress points,
while in the Network Function Virtualization Infrastructure (NFVI), the original
packet can be stripped of its headers (that could be saved in the session table)
to slightly improve internal packet transmission. \todo{Insert TCP session
  recreation schema} On top of that, it offers the possibility to use different
TCP flavours, hence increasing the communication speed in heterogeneous networks
(e.g. in case of satellite connections TCP Hybla can be employed, while it is
known that HighSpeed TCP gives best results when applied in optical fiber-based
connections).

>>>>

As in chapter~\ref{chap:intro}, the creation of a full ETSI MANO compliant
architecture, following the suggestions described in RFC 7665, require the
integration of multiple tools (some of them have been already briefly introduced
in~\ref{chap:intro}). The tools were choosen after their analysis, where pro and
cons have been studied and compared to the necessity of this thesis. Since the
project has been developed with the cloud provided by the University of Padua,
Openstack (which a product analysis can be found later
in~\ref{chap:prjan:sec:openstack}) has been used as base for our deployments.

@@

As today, when a packets gets send from a seder $S$, to a receiver $R$, the 
packet gets travelling to te backbone receive appropriate in-hardware packet 
processing before being received by $R$. During this elaboration, it is 
important to maintain the transparency of the connection, so that the network 
users are not aware of the packets elaboration at all. To perform that, many 
solutions are available: TUN/TAP packet incapsulation, IP over IP or TCP 
session recreation (know also as TCP split).

TUN/TAP and IP over IP maintain the connection transparency incapsulating the
packet in another one.
\begin{figure}[t]
  \centering
  \includegraphics[scale=0.5]{IPoverIP}
  \caption[IP over IP schema]{An example of IP over IP. Is noticeable how the
    original packet becomes the payload of a new one, thus being encapsulated.
    All the informations regarding the original packet remains untouched: when
    this kind of packet gets send from a machine to another, the OS will remove
    the new packet header and will present to the user-space program receiving
    the data its payload: a IP packet. Packets encapsulation can be applied with
    higher layers too, thus allowing for TCP and UDP packet incapsulation.}
  \label{chap:prjan:img:ip_over_ip}
\end{figure}

In this way, the original packet remains preserved and it becomes the new packet
payload\todo{Make an image showing a packet inside another packet, to make easy
  to understand what we're meaning here}, that can be elaborated and modified
accordingly, until it gets decapsulated and sent to $R$ eventually. When $R$
receives the packet, it is not be aware of the packet elaboration, since all the
original headers were preserved (or slightly modified). TCP session recreation,
instead, ``split'' the TCP session in two endpoints: an Ingress, that manage the
connection with the client and an Egress, that communicate with the packet
receiver creating a multi-overlay-hop path where for each hop there is an
possible indipendent TCP connection. In order to achieve that, a session table
needs to be established and continuously updated, while TCP headers need to be
accordingly modified to allow data transmission through the Ingress and Egress
points. Nonetheless, care should be given to packets path: in order to avoid
ill-calculated congestion windows, the incoming packets need to follow the same
(or an equivalent one) path for the same instatiated connection. This phenomenom
is based on the intermediate proxies that create the route: it is the case, for
example, when an intermediate node sends back a spoofed ACK before the original
packet is delivered to the real consegnee. In this senario, the sender, unaware
of the proxy, will miscalculate the sending window based on the too low RTT.
Other problems of TCP splitting are reliability and security, especially because
the end to end TCP logic is no longer maintained: a server failure may cause to
an unaware client to believe that all the packets have reached the destination.
TCP session recreation seems burdersome and it doesn't seem to add any
significant benefit at the first sight, but it offers the flexibility to perform
extensive packet manipulation: since the packet its recreated every time at the
Ingress and Egress points, while in the Network Function Virtualization
Infrastructure (NFVI), the original packet can be stripped of its headers (that
could be saved in the session table) to slightly improve internal packet
transmission. \todo{Insert TCP session recreation schema} On top of that, it
offers the possibility to use different TCP flavours, hence increasing the
communication speed in heterogeneous networks (e.g. in case of satellite
connections TCP Hybla can be employed, while it is known that HighSpeed TCP
gives best results when applied in optical fiber-based connections).
